As already specified, CMS maintains a huge amount of data, O(50PB), organized 
in datasets, which share common properties and users tend to analyze as a whole. 
Datasets are further subdivided into data blocks consisting of one or more files. These 
subdivisions facilitate the handling of the datasets.

A convenient set of tools exists to move data around but there is no intelligent tool to produce and
distribute copies of popular data or automatically remove less popular data. At present the various 
physics groups each have a data manager who is responsible for disk management. Usually this involves 
the management of about three Tier-2 computing sites and about a thousand 
datasets (mostly Monte Carlo simulation). Placement of new data is relatively straight forward but the 
deletion of older sets can be quite complicated and requires significant amount of time.

At MIT, we have tried to tackle this problem by considering a small subset of the CMS computing system, 
i.e. the two sites sub-system \{T2\_US\_MIT,T3\_US\_MIT\}. In this sub-system we have the following:

\begin{itemize}
	\item all datasets relevant for MIT analyses are stored on the Tier-2;
	\item all data analysis jobs are run on Tier-3 machines;
	\item the available disk space of the Tier-3 is not enough to store all datasets necessary for 
	the completion of all the analyses.
	\item users typically re-run a given analysis workflow multiple times on the same group of datasets in 
	a relatively short timescale.
\end{itemize}
We have designed and implemented an automated service, the \textbf{MIT HEP Dynamic Data (MITHDD)}, that 
caches the datasets on Tier-3, using the Tier-2 as a source pool. 

MITHDD is divided into two subservices: \textbf{SmartCache}, which is responsible for transferring 
datasets from Tier-2 to Tier-3, and \textbf{Cinderella}, which is responsible for deletions on Tier-3.

The source code of MITHDD follows the same structure and is currently available on \textsc{GitHub} at 
\href{https://github.com/cpausmit/DynamicData}{\textcolor{Mahogany}{this link}}. The software is licensed
under \href{http://opensource.org/licenses/MIT}{\textcolor{Mahogany}{these terms}}.

\subsection{SmartCache}\label{subsec:smartcache}
\input{smartcache.tex}

\subsection{Cinderella}\label{subsec:cinderella}
\input{cinderella.tex}





